R Notebook

### 2017-06-23 doc/RMD/data-comparison.Rmd
write raw and cleaned data to csv

```{r read_excel}
ex <- readxl::read_excel("../Analysis4 ForManu/A1_Copy of binned-genotypes_SE.xlsx", sheet = "GenAlex", skip = 1) %>%
  select(-1) %>%                # removing first column, which is empty
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove (F) designator
  mutate(allele = as.integer(allele)) %>% # force alleles to integers
  spread(locus, allele) %>%
  # slice(-n()) %>%
  I()
ex <- ex[!names(ex) %in% locNames(dat)]

@@

```{r merging_data}
corrected_loci <- ex %>% gather(locus, allele, -1) %>%
  left_join(exsummary, by = c("locus", "allele")) %>%
  mutate(allele = new_allele) %>%
  select(-new_allele) %>%
  spread(locus, allele) %>%
  separate(iso_st_mcg_org_loc_yr_hst_cult_rep, # Note: this corresponds closer to the initial data
           c("Isolate", "Severity", "MCG", "State", "Source", "Year", "Host"), 
           sep = "_") %>%
  arrange(Isolate) %>%
  select(-(Severity:Host))
datdf <- genind2df(dat, usepop = FALSE) %>% 
  rownames_to_column(var = "Isolate") %>% 
  left_join(corrected_loci, by = "Isolate")
stopifnot(identical(datdf$Isolate, indNames(dat)))
datdf <- datdf[c("Isolate", names(repeat_lengths))]
dat   <- datdf %>% 
  select(-Isolate) %>% 
  df2genind(ind.names = indNames(dat), strata = strata(dat), ploidy = 1) %>% 
  as.genclone()
```

>>>>

```{r read_excel}
ex <- readxl::read_excel("../Analysis4 ForManu/A1_Copy of binned-genotypes_SE.xlsx", sheet = "GenAlex", skip = 1) %>%
  select(-1) %>%                # removing first column, which is empty
  gather(locus, allele, -1) %>% # gather all loci into tidy columns
  mutate(locus = trimws(locus)) %>% # remove (F) designator
  mutate(allele = as.integer(allele)) %>% # force alleles to integers
  spread(locus, allele)

readr::write_csv(ex, "data/raw_data.csv", col_names = TRUE)

ex <- ex[!names(ex) %in% locNames(dat)]

@@

```{r merging_data}
corrected_loci <- ex %>% gather(locus, allele, -1) %>%
  left_join(exsummary, by = c("locus", "allele")) %>%
  mutate(allele = new_allele) %>%
  select(-new_allele) %>%
  spread(locus, allele) %>%
  separate(iso_st_mcg_org_loc_yr_hst_cult_rep, # Note: this corresponds closer to the initial data
           c("Isolate", "Severity", "MCG", "State", "Source", "Year", "Host"), 
           sep = "_") %>%
  arrange(Isolate) %>%
  select(-(Severity:Host))
datdf <- genind2df(dat, usepop = FALSE) %>% 
  rownames_to_column(var = "Isolate") %>% 
  left_join(corrected_loci, by = "Isolate")
stopifnot(identical(datdf$Isolate, indNames(dat)))
datdf <- datdf[c("Isolate", names(repeat_lengths))]
dat   <- datdf %>% 
  select(-Isolate) %>% 
  df2genind(ind.names = indNames(dat), strata = strata(dat), ploidy = 1) %>% 
  as.genclone()

strata(dat) %>%
  bind_cols(datdf) %>%
  as_data_frame() %>%
  readr::write_csv("data/clean_data.csv", col_names = TRUE)
```
